Inferring Lensing Mass in the Universe \\ from Photometric Catalog Data

### 2012-10-02 doc/paper-lcr.tex
draft update

For $\sumkappah$ to provide useful constraints on $\kapparay$, it is important that $\kapparay$ and $\sumkappah$ are as similar as possible. Figure \ref{fig:bias} shows that indeed $\sumkappah$ is a good estimator, regardless of the individual value of $\sumkappah$, although the scatter increases with $\sumkappah$.

\begin{figure}
\includegraphics[width=\columnwidth]{perfectc.eps}
\caption[Biased?]{$\$ minus $\kapparay$ as a function of $\kapparec$, for 10000 reconstructed lines of sight. The points are put into bins of width 0.01 in $\kapparec$, except the last bin containing all reconstructions with $\kapparec>0.14$. The errorbars show the population standard deviation for each bin. Since all of the errorbars are consistant with zero, there is no evidence for $\kapparec$ being a biased estimator of $\kapparay$}
\label{fig:isitbiased}
\end{figure}

>>>>

For $\sumkappah$ to provide useful constraints on $\kapparay$, it is important that $\kapparay$ and $\sumkappah$ are as similar as possible. Figure \ref{fig:bias} shows that indeed $\sumkappah$ is a good estimator, regardless of the individual value of $\sumkappah$. At fixed $\sumkappah$ we find that the scatter in $\kapparay$ grows with $\sumkappah$; our reconstruction is better at reproducing underdense lines of sight than overdense lines of sight.

\begin{figure}
\includegraphics[width=\columnwidth]{perfectc.eps}
\caption[Biased?]{$\sumkappah$ verses $\kapparay$ for 100000 reconstructed lines of sight. The points are put into bins of width 0.01 in $\kapparec$, except the last bin containing all reconstructions with $\kapparec>0.14$. The errorbars show the population standard deviation for each bin. Since all of the errorbars are consistant with zero, there is no evidence for $\kapparec$ being a biased estimator of $\kapparay$}
\label{fig:isitbiased}
\end{figure}
